Papers

### 2025-05-17 news.qmd
updates to multiple pages
add DOI

>>>>

<font color="#d08770">[May 14 2024].</font> **Paper accepted**. Sullivan SR, Lokesh R, Peters CS, Calalo J, Roth AR, Buggeln JH, Ngo TT, Carter MJ, &
Cashaback JGA. (In Press). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*. [https://doi.org/10.1152/jn.00563.2024](https://doi.org/10.1152/jn.00563.2024){target="_blank"}

### 2025-05-17 papers.qmd
add DOI

- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter, MJ. The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis. *International Review of Sport and Exercise Psychology*. ---
[{{< ai doi >}}](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-ee-optimal-theory){target="_blank" style="color: inherit;"}

@@

- St. Germain L., McKay B., Tandon C., Seedu J., Barbera L., Carrillo C., Brown DMY., & Carter, MJ. (2025). Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *Psychological Research*. ---
[{{< ai doi >}}](https://doi.org/10.1007/s00426-024-02059-z){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_st-germain-etal_autonomy-supportive-instructional-language-does-not-enhance-skill-acquisition-compared-to-controlling-instructional-language.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/expt_instructional-language){target="_blank" style="color: inherit;"}

>>>>

- Sullivan SR., Lokesh R., Peters CS., Calalo J., Roth AR., Buggeln JH., Ngo TT., Carter MJ., & Cashaback JGA. (In Press). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*. ---
[{{< ai doi >}}](https://doi.org/10.1152/jn.00563.2024){target="_blank" style="color: inherit;"}

- McKay B., Bacelar MFB., Parma JO., Miller MW., & Carter MJ. (In Press). The combination of reporting bias and underpowered study designs has substantially exaggerated the motor learning benefits of self-controlled practice and enhanced expectancies: A meta-analysis. *International Review of Sport and Exercise Psychology*. ---
[{{< ai doi >}}](https://doi.org/10.1080/1750984X.2023.2207255){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2023_mckay-etal_the-combination-of-reporting-bias-and-underpowered-study-designs-has-substantially-exaggerated-the-motor-learning-benefits-of.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/proj_sc-ee-optimal-theory){target="_blank" style="color: inherit;"}

@@

- St. Germain L., McKay B., Tandon C., Seedu J., Barbera L., Carrillo C., Brown DMY., & Carter MJ. (2025). Autonomy-supportive instructional language does not enhance skill acquisition compared to controlling instructional language. *Psychological Research*. ---
[{{< ai doi >}}](https://doi.org/10.1007/s00426-024-02059-z){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_st-germain-etal_autonomy-supportive-instructional-language-does-not-enhance-skill-acquisition-compared-to-controlling-instructional-language.pdf){target="_blank" style="color: inherit;"}
[{{< fa brands github >}}](https://github.com/cartermaclab/expt_instructional-language){target="_blank" style="color: inherit;"}
